Simple connectome inference from partial correlation statistics\\in calcium imaging

### 2014-11-07 spotlight/spotlight.tex
spotlight final version

\textbf{{\color{i6blue}Goal:}} From time-series of the neuron activity, infer the directed connections between neurons.\\[1.5ex]
%This is {\color{red} difficult} task.\\[2ex]
\textbf{{\color{red}But:}} This is not that easy because of the nature of the data.\\[1.5ex]

@@

\textbf{{\color{i6blue} Steps of our solution:}}
\begin{enumerate}[{\color{i6blue} 1.}]
\item Signal processing\\{\scriptsize(deal with calcium fluorescent signals)}
\item Averaged partial correlation statistics\\{\scriptsize(find the undirected network)}
\item Prediction of edge orientation
\end{enumerate}

>>>>

\textbf{{\color{i6blue}Goal:}} From time-series of the neuron activity, \textbf{infer} the directed \textbf{connections between neurons}.\\[1ex]
%This is {\color{red} difficult} task.\\[2ex]
\textbf{{\color{i6blue}Results:}} Our method was the \textbf{best} performer in the recent \textit{Neural Connectomics Challenge}.\\[1ex]

@@

\textbf{{\color{green} Steps of our solution:}}
\begin{enumerate}[{\color{i6blue} 1.}]
\item Signal processing\\{\scriptsize(deal with calcium fluorescent signals)}
\item Averaged partial correlation statistics\\{\scriptsize(find the undirected network)}
\item Prediction of edge orientation
\end{enumerate}
